Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Edits.

The experimental Tor Browser releases have all used Google as the intermediate web service.
Support for CloudFront was not realized until late July.
We are running the backends on paid accounts for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total App Engine bill so far has been \$2.07.
There has not yet been enough use of CloudFront to cost any money.
A longer-term goal is to find a way to fund continued operation
if the system becomes popular.

@@

@@

When domain fronting is combined with Tor,
the CDN or web service effectively becomes
what Tor calls a ``guard node,''
a host with a privileged network position that can observe
the ciphertext entering the network.
One consequence of this fact is that Google (for example)
knows the IP addresses of everyone using the circumvention system,
just as if it were those users' ISP.
Another consequence is that the CDN or web service gets
to observe and correlate both entry and exit traffic,
in the special case where the target of the communication
also lies on the same CDN or web service.
For example, a user fronting through App Engine and
browsing YouTube reveals both their entry and exit traffic to Google,
which may attempt through traffic analysis to determine
which entry packets correspond to which exit packets.
The problem is hard to counter, because the front domain needs
to be popular in order to have high collateral damage,
but popular domains are also the ones people tend to want to go to.
% Possible countermeasure is traffic fingerprinting resistance
% like what mjuarez is working on, mostly orthogonal to circumvention.

@@

The key idea of meek is domain fronting,
but its HTTP-tunneling ability is useful on its own.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN could
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from App Engine.

Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
In this scenario, Google still has a privileged network position,
but the user's traffic patterns are no longer visible to the operators of a public app instance.
% Outgoing HTTP requests include app id? As good as an IP address.

>>>>

@@

The experimental Tor Browser releases have all used Google with App Engine as the intermediate web service.
Support for CloudFront was not realized until late July.
We are running the backends on paid accounts for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total App Engine bill so far has been \$2.07,
with most days' usage being below the billable threshold.
There has not yet been enough use of CloudFront to cost anything.

A longer-term goal is to find a way to fund continued operation
if the system becomes popular.
Although some of the systems listed in Section~\ref{sec:survey}
are inexpensive enough that some users could upload their own fronting backend,
thereby diffusing costs,
we believe that an organization operating a backend for the use of the public
has compelling usability advantages.
With client software can be configured to use the public backend by default,
there is nothing for the user to upload and no out-of-band communication is needed before getting
started---if everything works it offers no-configure circumvention.

% The number of parties able to analyze users' traffic patterns is somewhat increased:
% the path from user to Tor bridge now includes App Engine and the web app operators,
% in addition to the ISP and intermediate routers that were there before.
% On the other hand, the Tor bridge no longer gets to see users' IP addresses:
% all it sees are many connections from App Engine.

@@

The intermediate web service enjoys a privileged network position
from which it is able to monitor all circumvention traffic.
Even if the censor doesn't know who the users are, the CDN knows.
The web service has basically the same network visibility
as a client's ISP would have if the client were connecting to Tor directly.
For this reason, domain fronting should be combined with another
layer, for example Tor, that prevents the web service from
observing the contents and destination of messages.
There is additional risk when the client is browsing a web site
controlled by the same service as that they are fronting through,
for example browsing YouTube while fronting through \urll{www.google.com}.
Even with Tor, in this case the web service gets to see
both entry and exit traffic, and is in a position to
perform traffic correlation attacks.
The problem seems hard to counter, because the front domain needs
to be popular in order to have high collateral damage,
but popular domains are also the ones people tend to want to go to.
A possible mitigation is traffic obfuscation that lasts all
the way to the second hop of a three-hop Tor circuit,
which would reduce the correlation between entry and exit traffic.
% like what mjuarez is working on, mostly orthogonal to circumvention.

@@

The key idea of meek is domain fronting,
but its HTTP tunneling ability is useful on its own.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN could
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.
